---
title       : Parsing functions in readr
description : Once you have successfully imported your data, you may need to change the type of one or more columns.

--- type:NormalExercise lang:r xp:100 skills:1 key:ddabbd341d
## Coercing columns to different data types

The import functions in `readr` are quite good at guessing the correct data types for each column in a dataset.  Of course, they aren't perfect, so sometimes you will need to change the type of a column after importing.

You might also find that the way your data is encoded prevented `readr` from assigning it the desired type.  If your dataset stores dates like August 12, 2016 as `20160812`, it will of course be read as an integer.

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec
```

*** =sample_code
```{r}
# sample code
```

*** =solution
```{r}
# solution code
```

*** =sct
```{r}
success_msg("Great work!")
```

--- type:NormalExercise lang:r xp:100 skills:1 key:4d212a1085
## Coercing character columns into factors

Use parse_factor to interpret columns from professor salaries as factors.

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec
```

*** =sample_code
```{r}
# sample code
```

*** =solution
```{r}
# solution code
```

*** =sct
```{r}
success_msg("Great work!")
```

--- type:NormalExercise lang:r xp:100 skills:1 key:ae367ecf0a
## Creating Date objects

Use parse_date to create Date columns in weather data.

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec
```

*** =sample_code
```{r}
# sample code
```

*** =solution
```{r}
# solution code
```

*** =sct
```{r}
success_msg("Great work!")
```

--- type:NormalExercise lang:r xp:100 skills:1 key:3ace73122f
## Parsing number formats

Use parse_number to interpret national debt data as currency and numbers with commas.

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec
```

*** =sample_code
```{r}
# sample code
```

*** =solution
```{r}
# solution code
```

*** =sct
```{r}
success_msg("Great work!")
```

--- type:NormalExercise lang:r xp:100 skills:1 key:74ee790657
## Saving metadata to the disk

Use spec_delim() to preserve metadata to be imported later.

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec
```

*** =sample_code
```{r}
# sample code
```

*** =solution
```{r}
# solution code
```

*** =sct
```{r}
success_msg("Great work!")
```

--- type:NormalExercise lang:r xp:100 skills:1 key:832bd3d11f
## Importing metadata

Recover metadata from the previous exercise.

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec
```

*** =sample_code
```{r}
# sample code
```

*** =solution
```{r}
# solution code
```

*** =sct
```{r}
success_msg("Great work!")
```

