---
title       : Parsing functions in readr
description : Once you have successfully imported your data, you may need to change the type of one or more columns.

--- type:NormalExercise lang:r xp:100 skills:1 key:ddabbd341d
## Coercing columns to different data types

The import functions in `readr` are quite good at guessing the correct data types for each column in a dataset.  Of course, they aren't perfect, so sometimes you will need to change the type of a column after importing.

You might also find that the way your data is encoded prevented `readr` from assigning it the desired type.  If your dataset stores dates like August 12, 2016 as `20160812`, it will of course be read as an integer.  You could then insert dashes at the appropriate locations and call `type_convert()` to ask `readr` to try parsing again.

In this exercise, you'll be calling `type_convert()` using a column specification you create.  This is a manual override and should not be needed often.  To create the column specification, you'll use `cols()` as follows:

```
# Converts each column to specified type (i for int, d for double, etc.)
new_df <- type_convert(df, col_types = cols(col1 = "d", col2 = ...))
```

*** =instructions
Use `type_convert` to change all columns of `trees` (`Girth`, `Height`, and `Volume`) to doubles.  Assign the resulting data frame to the name `trees2`.

*** =hint
`type_convert()` should take two arguments:
- A data frame, `trees`
- The result of a function call: `cols(Girth = "d", Height = "d", Volume = "d")`

*** =pre_exercise_code
```{r}
library(readr)
trees <- read_csv2("http://s3.amazonaws.com/assets.datacamp.com/production/course_1561/datasets/trees.csv")
```

*** =sample_code
```{r}
## trees is pre-loaded

# Convert all columns to double
trees2 <- type_convert(trees, col_types = cols(Girth = "d", Height = "d", Volume = "d"))
```

*** =solution
```{r}
## trees is pre-loaded

# Convert all columns to double
trees2 <- type_convert(trees, col_types = cols(Girth = "d", Height = "d", Volume = "d"))
```

*** =sct
```{r}
test_correct({test_object("trees2")}, 
             {
                 test_function("type_convert", 
                               args = c("df", "col_types"), 
                               eval = FALSE)
                 test_error()
             })
test_error()
success_msg("Great work!")
```

--- type:NormalExercise lang:r xp:100 skills:1 key:4d212a1085
## Coercing character columns into factors

As you saw in the last chapter, one of the features of `readr` import functions is that they don't automatically convert all strings into factors like `read.csv()` does.  Sometimes, though, you want one or more columns of data to be interpreted as factors.

In those situations, you can use `parse_factor()` after importing your data.  You need to supply the column to be parsed and a vector of possible values as arguments to your call.  In this case, you'll be parsing the `title` and `gender` columns of pre-loaded data frame `salaries`.

*** =instructions
- Use `parse_factor()` to convert the `title` column of `salaries` to a factor.  Supply `c("Prof", "AsstProf", "AssocProf")` as the `levels` argument.  Assign the result of the function call back to `salaries$title`.
- Use the same function to parse the `gender` column of `salaries`.  Supply `c("Male", "Female")` as the `levels` argument.  Assign the result to `salaries$gender`.

*** =hint
Both calls to `parse_factor()` should take two arguments.  The first argument should be the column to be parsed.  The second argument should be the given character vector.

*** =pre_exercise_code
```{r}
library(readr)
salaries <- read_tsv("http://s3.amazonaws.com/assets.datacamp.com/production/course_1561/datasets/Salaries.txt", col_names = FALSE, col_types = cols(
    X2 = col_skip(),
    X3 = col_skip(), 
    X4 = col_skip()
))
names(salaries) <- c("title", "gender", "salary")
```

*** =sample_code
```{r}
# Parse the title column
salaries$title <- parse_factor(salaries$title, levels = c("Prof", "AsstProf", "AssocProf"))

# Parse the gender column
salaries$gender <- parse_factor(salaries$gender, levels = c("Male", "Female"))
```

*** =solution
```{r}
# Parse the title column
salaries$title <- parse_factor(salaries$title, levels = c("Prof", "AsstProf", "AssocProf"))

# Parse the gender column
salaries$gender <- parse_factor(salaries$gender, levels = c("Male", "Female"))
```

*** =sct
```{r}
test_function("parse_factor", args = c("x", "levels"), index = 1, eval = FALSE)
test_function("parse_factor", args = c("x", "levels"), index = 2, eval = FALSE)
success_msg("Great work!")
```

--- type:NormalExercise lang:r xp:100 skills:1 key:ae367ecf0a
## Creating Date objects

The `readr` import functions can automatically recognize dates in standard ISO 8601 format (YYYY-MM-DD) and parse columns accordingly.  If you want to import a dataset with dates in other formats, you can use `parse_date()`.

In this exercise, you'll be working with some weather data.  Each date is stored according to American convention: MM/DD/YYYY.  In order to specify this format, you'll use `%m` for two-digit month, `%d` for two-digit day, and `%Y` for four-digit year.

*** =instructions
Parse the `date` column of pre-loaded data frame `weather` using `parse_date()`.  Set the `format` argument to `"%m/%d/%Y"`, and assign the result back to the `date` column.

*** =hint
`parse_date()` should take the `date` column of `weather` and `"%m/%d/%Y"` as arguments.

*** =pre_exercise_code
```{r}
library(readr)
weather <- read_csv("http://s3.amazonaws.com/assets.datacamp.com/production/course_1561/datasets/weather.csv")
```

*** =sample_code
```{r}
# Change type of date column
weather$date <- parse_date(weather$date, format = "%m/%d/%Y")
```

*** =solution
```{r}
# Change type of date column
weather$date <- parse_date(weather$date, format = "%m/%d/%Y")
```

*** =sct
```{r}
test_correct({test_object("weather")}, 
             {
                 test_function("parse_date", args = c("x", "format"), 
                               eval = FALSE)
                 test_error()
             })
test_error()
success_msg("Great work!")
```

--- type:NormalExercise lang:r xp:100 skills:1 key:3ace73122f
## Parsing number formats

The `readr` importing functions can sometimes run into trouble parsing a column as numbers when it contains non-numeric symbols in addition to numerals.

For example, we loaded a data frame called `debt` containing the national debt of the US in different years.  Take a look at `head(debt)` to see that even the debt amount is stored as characters.

Your job is to use `parse_number()` to coerce the `amount` column containing debt values to numeric.

*** =instructions
Use `parse_number()` to interpret the `amount` column of the pre-loaded `debt` data frame.  Assign the result of the funciton call back to the `amount` column.

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
library(readr)
debt <- read_csv("http://s3.amazonaws.com/assets.datacamp.com/production/course_1561/datasets/national_debt.csv")
names(debt) <- c("date", "amount")
```

*** =sample_code
```{r}
# Parse amount column as a number
debt$amount <- parse_number(debt$amount)
```

*** =solution
```{r}
# Parse amount column as a number
debt$amount <- parse_number(debt$amount)
```

*** =sct
```{r}
test_correct({test_object("debt")}, 
             {
                 test_function("parse_number", args = "x", eval = FALSE)
                 test_error()
             })
test_error()
success_msg("Great work!")
```

--- type:NormalExercise lang:r xp:100 skills:1 key:74ee790657
## Viewing metadata before importing

In some cases, it may be easier to get an idea of how `readr` plans to parse a dataset before you actually import it.  When you see the planned column specification, you might decide to change the type of one or more columns, for example.

`spec` functions exist for .csv and .tsv files, and for other file types by using the `delim` argument in `spec_delim()`.

In this final exercise, you'll use `spec_csv` to get a preview of how `chickwts.csv` would be imported.

*** =instructions
Use `spec_csv` to determine how `chickwts.csv` will be parsed upon import.  Simply print the specification to the console.

*** =hint
`spec_csv` just takes one argument: a file name in quotes.

*** =pre_exercise_code
```{r}
library(readr)
download.file("http://s3.amazonaws.com/assets.datacamp.com/production/course_1561/datasets/chickwts.csv", "chickwts.csv")
```

*** =sample_code
```{r}
# Specifications of chickwts
spec_csv("chickwts.csv")
```

*** =solution
```{r}
# Specifications of chickwts
spec_csv("chickwts.csv")
```

*** =sct
```{r}
test_output_contains(spec_csv("chickwts.csv"))
success_msg("Great work!")
```
