---
title       : Importing data with readr
description : This chapter covers all the useful `readr` functions that reads in data.

--- type:NormalExercise lang:r xp:100 skills:1 key:086558b449
## Reading a .csv file

Welcome to this mini-course on the `readr` package!  Over the next two chapters, you’ll be exposed to many of the great features this chapter has to offer.

Let’s get started right away with some basic importing features.  Your first task will be to master the use of the `read_csv()` function.  There are many arguments available, but the only required argument is `file`, a path to a CSV file on the disk.

You’ll be practicing your importing skills on a dataset containing weights of chickens and their feed type.

*** =instructions
- Load the `readr` package.
- Use the `read_csv()` function to import `chickwts.csv`.  Call the resulting data frame `cwts`.
- View the `head()` of `cwts`.

*** =hint
Your call to `read_csv()` should take one argument: the name of the CSV file, in quotes.

*** =pre_exercise_code
```{r}
download.file("http://s3.amazonaws.com/assets.datacamp.com/production/course_1561/datasets/chickwts.csv", "chickwts.csv")
```

*** =sample_code
```{r}
# Load readr
library(readr)

# Import chickwts.csv: cwts
cwts <- read_csv("chickwts.csv")

# View the head of cwts
head(cwts)
```

*** =solution
```{r}
# Load readr
library(readr)

# Import chickwts.csv: cwts
cwts <- read_csv("chickwts.csv")

# View the head of cwts
head(cwts)
```

*** =sct
```{r}
test_library_function("readr")
test_function("read_csv")
test_output_contains("head(cwts)")
test_error()
success_msg("Great work!")
```

--- type:NormalExercise lang:r xp:100 skills:1 key:5c4acd4138
## Reading a .tsv file

In the previous exercise, you might have noticed this message when you called `read_csv()`:

```
Parsed with column specification:
cols(
  weight = col_integer(),
  feed = col_character()
)
```

This occurs every time any `readr` function is called to import data. In fact, all `readr` functions that imports data has the argument `col_type`, which allows for custom column specifications. The message shows how the `col_type` argument was specified by default. Notice the column specification is created by `cols()` and in it, are the names of the columns and a `col_*()` function that tells R to import it as the `*`. For example, the `weight` column was imported as `integer` and the `feed` column as `character` by default. One special `col_*()` function is the `col_skip()` column, which tells R to skip that column when importing the data.

All `readr` functions that imports data also has the argument `col_names` which is used when you want to name the columns different from what's in the data file. This argument takes in either `TRUE`, `FALSE`, or a character vector of column names. If set equal to `TRUE`, the first row of the input will be used as the column names. If `FALSE`, column names will be generated automatically: `X1`, `X2`, `X3`, etc. If `col_names` is a character vector, the values will be used as the names of the columns, and the first row of the input will be read into the first row of the output data frame.

These arguments are useful when you know you want to import certain columns of the data as certain types with certain names. The `readr` package does a great job guessing what each column type and name should be, but it's important to know that you can also customize this further with the `col_names` and `col_type` arguments.

In this exercise, you’ll import a set of data on professors’ salaries called `Salaries.tsv` with `read_tsv()`, another `readr` function that imports files with tab-separated values. This time, you’ll also provide custom column specifications when you're reading in the data.

*** =instructions
The `readr` package is loaded in your workspace.

- Use the `read_tsv()` function to read in the `Salaries.tsv` file with a custom `cols()` specification that tells R to autogenerate column names skip columns `X2`, `X3`, and `X4`. Store the result in an object called `salaries`.
- View the `head()` of `salaries`.

*** =hint
Don't forget to specify the `file` argument to `read_tsv()` in quotes!

*** =pre_exercise_code
```{r}
library(readr)

# Change file extension when downloading
# Workaround because teach app appears not to recognize TSV files
download.file("http://s3.amazonaws.com/assets.datacamp.com/production/course_1561/datasets/Salaries.txt", "Salaries.tsv")
```

*** =sample_code
```{r}
## readr is loaded

# Import data: salaries
salaries <- read_tsv("Salaries.tsv", col_names = FALSE, col_types = cols(
    X2 = col_skip(),
    X3 = col_skip(), 
    X4 = col_skip()
))

# View first six rows of salaries
head(salaries)
```

*** =solution
```{r}
## readr is loaded

# Import data: salaries
salaries <- read_tsv("Salaries.tsv", col_names = FALSE, col_types = cols(
    X2 = col_skip(),
    X3 = col_skip(), 
    X4 = col_skip()
))

# View first six rows of salaries
head(salaries)
```

*** =sct
```{r}
test_function("read_tsv", args = c("file", "col_names", "col_types"), not_called_msg = "Don't forget to call `read_tsv()` to import your data.")
test_function("head", incorrect_msg = "Did you print the first six rows of `salaries` using `head()`?")
test_error()
success_msg("Nice work! The `readr` package makes importing data a lot more efficient with arguments that allows more flexibility. In the next exercise, you'll learn about another `readr` function, the `read_csv2()` function, used to import European data.")
```

--- type:NormalExercise lang:r xp:100 skills:1 key:26f83a8842
## Reading a European .csv

In most of Europe, commas (rather than periods) are used as decimal points.  This creates an issue for comma-separated value files: since commas can no longer be used to separate values, semicolons are used instead.

For this reason, `readr` provides `read_csv2()` which looks for `;` to indicate column breaks and `,` to indicate decimal points.  Other than that, it behaves just like `read_csv()`.

In this exercise, you'll see what happens when you incorrectly use `read_csv()` on datasets that contain values separated by semicolons. You'll import a dataset that contains information on the girth, height, and volume for Black Cherry Trees.

*** =instructions
The `readr` package and the `trees.csv` file are already loaded in your workspace.

- Correctly import `trees.csv` with the `read_csv2()` function and store the result as `trees`.
- View the dimensions of `trees` using the `dim()` function and print the first six rows of `trees` to the console.
- Now incorrectly import the data with `read_csv()` and store the result as `trees_wrong`.
- View the dimensions of `trees_wrong` using the `dim()` function and print the first six rows of `trees_wrong` to the console.

*** =hint
The `read_csv()` and `read_csv2()` functions have the same syntax. Specify the `file` argument to both calls and make sure they're in quotes!

*** =pre_exercise_code
```{r}
library(readr)
download.file("http://s3.amazonaws.com/assets.datacamp.com/production/course_1561/datasets/trees.csv", "trees.csv")
```

*** =sample_code
```{r}
# Import data with read_csv2()
trees <- read_csv2("trees.csv")

# View dimensions and head: trees
dim(trees)
head(trees)

# Import data with read_csv()
trees_wrong <- read_csv("trees.csv")

# View dimensions and head: trees_wrong
dim(trees_wrong)
head(trees_wrong)
```

*** =solution
```{r}
# Import data with read_csv2()
trees <- read_csv2("trees.csv")

# View dimensions and head: trees
dim(trees)
head(trees)

# Import data with read_csv()
trees_wrong <- read_csv("trees.csv")

# View dimensions and head: trees_wrong
dim(trees_wrong)
head(trees_wrong)
```

*** =sct
```{r}
test_data_frame("trees", undefined_msg = "Don't forget to create `trees`!", incorrect_msg = "Did you import your data with `read_csv2()` to create `trees`?")
test_function("read_csv2", incorrect_msg = "Did you import your data with `read_csv2()` to create `trees`?", not_called_msg = "Don't forget to import your data with `read_csv2()` to create `trees`!")

test_output_contains("dim(trees)", incorrect_msg = "Did you print out the dimensions of `trees`?")
test_output_contains("head(trees)", incorrect_msg = "Did you print the `head()` of `trees` to the console?")

test_data_frame("trees_wrong", undefined_msg = "Don't forget to create `trees_wrong`!", incorrect_msg = "Did you import your data with `read_csv()` to create `trees_wrong`?")
test_function("read_csv", incorrect_msg = "Did you import your data with `read_csv()` to create `trees_wrong`?", not_called_msg = "Don't forget to import your data with `read_csv()` to create `trees_wrong`!")

test_output_contains("dim(trees_wrong)", incorrect_msg = "Did you print out the dimensions of `trees_wrong`?")
test_output_contains("head(trees_wrong)", incorrect_msg = "Did you print the `head()` of `trees_wrong` to the console?")

test_error()
success_msg("Excellent work! The `read_csv()` function combined the three columns into one called `Girth; Height; Volume` because it couldn't recognize how the values were separated. If you see something like this in the future, now you know how to fix it!")
```

--- type:NormalExercise lang:r xp:100 skills:1 key:a44d920a83
## Read a fixed-width file

Use `read_table()` to import a directory of some famous names.  Then use `read_fwf()` to make use of the `skip` and `na` arguments.

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
library(readr)
download.file("http://s3.amazonaws.com/assets.datacamp.com/production/course_1561/datasets/names.txt", "names.csv")
```

*** =sample_code
```{r}
# sample code
```

*** =solution
```{r}
# solution code
```

*** =sct
```{r}
success_msg("Great work!")
```

--- type:NormalExercise lang:r xp:100 skills:1 key:86feb802cd
## Reading a text file

Use read_file and read_lines to import tweets into R.

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
library(readr)
```

*** =sample_code
```{r}
# sample code
```

*** =solution
```{r}
# solution code
```

*** =sct
```{r}
success_msg("Great work!")
```

--- type:NormalExercise lang:r xp:100 skills:1 key:1475b4009c
## Writing .csv and .tsv files

After importing and working with a data set, you'll want to save it off to the disk to make sure that your hard work doesn't go to waste.  In this exercise, you'll learn how.

If you've used `write.csv()` in the base package, you may have noticed that by default, row numbers are inserted as the leftmost column.  Then when you import back into R, the row numbers show up as a column of data.

Not so with `write_csv()`, the equivalent function in the `readr` package.  No duplicate row numbers are added.  As with other functions you've seen, `write_csv()` has many optional arguments, but the required ones are `x` and `path`.

Take a look at the other arguments using `?write_csv`.  Notice especially that because the default value of `col_names` is `!append`, switching to `append` mode (add to the end of a pre-existing file) automatically disables the writing of column names, unless you manually override both.  Makes sense, right?

*** =instructions
- Use `write_csv()` to save the `cwts` data set as `chickwts.csv`.
- Save `cwts2`, which has more chicken data, using the same function and file name, but this time set the `append` argument to `TRUE`.

*** =hint
Your first call to `write_csv()` should take two arguments: a data frame and a new file name in quotes.  Your second call should take three arguments: a data frame, a pre-existing file name in quotes, and `append = TRUE`.

*** =pre_exercise_code
```{r}
library(readr)

cwts <- read_csv("http://s3.amazonaws.com/assets.datacamp.com/production/course_1561/datasets/chickwts.csv")

cwts2 <- read_csv("http://s3.amazonaws.com/assets.datacamp.com/production/course_1561/datasets/chickwts2.csv")
```

*** =sample_code
```{r}
# Save cwts as chickwts.csv
write_csv(cwts, "chickwts.csv")

# Append cwts2 to chickwts.csv
write_csv(cwts2, "chickwts.csv", append = TRUE)
```

*** =solution
```{r}
# Save cwts as chickwts.csv
write_csv(cwts, "chickwts.csv")

# Append cwts2 to chickwts.csv
write_csv(cwts2, "chickwts.csv", append = TRUE)
```

*** =sct
```{r}
test_function("write_csv", args = c("x", "path"), index = 1)
test_function("write_csv", args = c("x", "path", "append"), index = 2)
success_msg("Great work!")
```

--- type:NormalExercise lang:r xp:100 skills:1 key:79bb8b3329
## Writing .rds files

Sometimes, saving to a CSV file just won't cut it.  If the R object you're working with has metadata associated with it, saving to a CSV will cause that information to be lost.

For example, if your dataset has one column of factors and other columns with characters, there will be no easy way to restore that metadata from a CSV.

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
library(readr)
```

*** =sample_code
```{r}
# sample code
```

*** =solution
```{r}
# solution code
```

*** =sct
```{r}
success_msg("Great work!")
```

