---
title       : Importing data with readr
description : This chapter covers all the useful `readr` functions that reads in data.

--- type:NormalExercise lang:r xp:100 skills:1
## Reading a .csv file

Use read_csv to import chick weight data.  Note automatic coercion of columns for some; coerce others manually.

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec
```

*** =sample_code
```{r}
# sample code
```

*** =solution
```{r}
# solution code
```

*** =sct
```{r}
success_msg("Great work!")
```

--- type:NormalExercise lang:r xp:100 skills:1
## Reading a .tsv file

Use read_tsv to import salary info.  Add a col_names argument to specify column names.

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec
```

*** =sample_code
```{r}
# sample code
```

*** =solution
```{r}
# solution code
```

*** =sct
```{r}
success_msg("Great work!")
```

--- type:NormalExercise lang:r xp:100 skills:1
## Reading a European .csv

Use read_csv2 to import a semicolon-delimited file containing tree measurements.

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec
```

*** =sample_code
```{r}
# sample code
```

*** =solution
```{r}
# solution code
```

*** =sct
```{r}
success_msg("Great work!")
```

--- type:NormalExercise lang:r xp:100 skills:1
## Read a fixed-width file

Use read_table to import a directory of some famous names.  Then use read_fwf to make use of the skip and na arguments.

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec
```

*** =sample_code
```{r}
# sample code
```

*** =solution
```{r}
# solution code
```

*** =sct
```{r}
success_msg("Great work!")
```

--- type:NormalExercise lang:r xp:100 skills:1
## Reading a text file

Use read_file and read_lines to import tweets into R.

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec
```

*** =sample_code
```{r}
# sample code
```

*** =solution
```{r}
# solution code
```

*** =sct
```{r}
success_msg("Great work!")
```

--- type:NormalExercise lang:r xp:100 skills:1
## Writing .csv and .tsv files

Use write_csv and write_tsv to save data frames to the disk.

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec
```

*** =sample_code
```{r}
# sample code
```

*** =solution
```{r}
# solution code
```

*** =sct
```{r}
success_msg("Great work!")
```

--- type:NormalExercise lang:r xp:100 skills:1
## Writing .rds files

Use write_rds to preserve metadata about R objects.

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec
```

*** =sample_code
```{r}
# sample code
```

*** =solution
```{r}
# solution code
```

*** =sct
```{r}
success_msg("Great work!")
```

