---
title       : Importing data with readr
description : This chapter covers all the useful `readr` functions that reads in data.

--- type:NormalExercise lang:r xp:100 skills:1
## Reading a .csv file

Welcome to this mini-course on the `readr` package!  Over the next two chapters, you’ll be exposed to many of the great features this chapter has to offer.

Let’s get started right away with some basic importing features.  Your first task will be to master the use of the `read_csv()` function.  There are many arguments available, but the only required argument is `file`, a path to a CSV file on the disk.

You’ll be practicing your importing skills on a dataset containing weights of chickens and their feed type.

*** =instructions
- Load the `readr` package (already installed on DataCamp).
- Use the `read_csv()` function to import `chickwts.csv`.  Call the resulting data frame `cwts`.
- View the `head()` of `cwts`.

*** =hint
Your call to `read_csv()` should take one argument: the name of the CSV file, in quotes.

*** =pre_exercise_code
```{r}
## TODO: insert link from teach app
```

*** =sample_code
```{r}
# Load readr
library(readr)

# Import chickwts.csv: cwts
read_csv("chickwts.csv")

# View the head of cwts
head(cwts)
```

*** =solution
```{r}
# Load readr
library(readr)

# Import chickwts.csv: cwts
read_csv("chickwts.csv")

# View the head of cwts
head(cwts)
```

*** =sct
```{r}
test_library_function("readr")
test_function("read_csv")
test_output_contains("head(cwts)")
test_error()
success_msg("Great work!")
```

--- type:NormalExercise lang:r xp:100 skills:1
## Reading a .tsv file

If your file happens to be tab-delimited, `readr` offers a function specifically for that purpose.  `read_tsv()` uses a TSV file to produce a data frame in R.

`read_tsv()` behaves almost identically to `read_csv()`.  There are many optional arguments and one required argument, `file`.

In this exercise, you’ll import a set of data on professors’ salaries called `Salaries.tsv`.  This time, we’ll also explore a couple of optional arguments.

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec
```

*** =sample_code
```{r}
# sample code
```

*** =solution
```{r}
# solution code
```

*** =sct
```{r}
success_msg("Great work!")
```

--- type:NormalExercise lang:r xp:100 skills:1
## Reading a European .csv

In most of Europe, commas (rather than periods) are used as decimal points.  This creates an issue for comma-separated value files: since commas can no longer be used to separate values, semicolons are used instead.

For this reason, `readr` provides `read_csv2()` which looks for `;` to indicate column breaks and `,` to indicate decimal points.  Other than that, it behaves just like `read_csv()`

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec
```

*** =sample_code
```{r}
# sample code
```

*** =solution
```{r}
# solution code
```

*** =sct
```{r}
success_msg("Great work!")
```

--- type:NormalExercise lang:r xp:100 skills:1
## Read a fixed-width file

Use read_table to import a directory of some famous names.  Then use read_fwf to make use of the skip and na arguments.

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec
```

*** =sample_code
```{r}
# sample code
```

*** =solution
```{r}
# solution code
```

*** =sct
```{r}
success_msg("Great work!")
```

--- type:NormalExercise lang:r xp:100 skills:1
## Reading a text file

Use read_file and read_lines to import tweets into R.

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec
```

*** =sample_code
```{r}
# sample code
```

*** =solution
```{r}
# solution code
```

*** =sct
```{r}
success_msg("Great work!")
```

--- type:NormalExercise lang:r xp:100 skills:1
## Writing .csv and .tsv files

Use write_csv and write_tsv to save data frames to the disk.

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec
```

*** =sample_code
```{r}
# sample code
```

*** =solution
```{r}
# solution code
```

*** =sct
```{r}
success_msg("Great work!")
```

--- type:NormalExercise lang:r xp:100 skills:1
## Writing .rds files

Use write_rds to preserve metadata about R objects.

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec
```

*** =sample_code
```{r}
# sample code
```

*** =solution
```{r}
# solution code
```

*** =sct
```{r}
success_msg("Great work!")
```

